3D Magnetic modelling of ellipsoidal bodies

### 2017-01-17 manuscript/manuscript.tex
problema na matriz de suscetibilidade

@@

A last but not least set of parameters defining the geometry of
an ellipsoid are their focal points.
The focal points are defined on the axes of the local coordinate 
system as follows:
\begin{equation}
\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
\begin{cases}
\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
\end{cases} \: .
\label{eq:focal-points}
\end{equation}
All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.

\subsection{Auxiliary variable $\lambda$}

@@

\bibliographystyle{copernicus}
\bibliography{references}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{references.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

>>>>

\citep{dubois1896}: The magnetisation induced in a uniform field is not necessarily 
also uniform.
A vector is said to be distributed uniformly when at
every point throughout the region considered it has the same
direction and the same value.
It maybe mathematically proved that such
uniformity only holds for bodies of an ellipsoidal shape.
If one axis coincides with the direction of the field, 
the magnetisation is in the same direction as that axis.
The demagnetising intensity for unit magnetisation we 
shall again speak of as the demagnetising
factor for the axial direction in question.

@@

%A last but not least set of parameters defining the geometry of
%an ellipsoid are their focal points.
%The focal points are defined on the axes of the local coordinate 
%system as follows:
%\begin{equation}
%\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
%\begin{cases}
%\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
%\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
%\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
%\end{cases} \: .
%\label{eq:focal-points}
%\end{equation}
%All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.

\subsection{Magnetic scalar potential }

@@

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{references}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}
